Fivebranes

### 2022-05-17 fivebranes/twisted.tex
changes

\subsection{Observables in a holomorphic-topological theory}

One of the main results of \cite{CG2}.

\begin{dfn} 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
\end{dfn}

\parsec

Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
\[
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\]
where $L$ is a graded holomorphic vector bundle on $X$.

\begin{lem}
\label{lem:localops}
Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
Then, the Taylor expansion map
\[
\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
\]
induces a quasi-isomorphism of commutative dg algebras
\[
\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
\]
\end{lem}

@@

Let $X$ be a Calabi--Yau five-fold. 
In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given. 
Within the BV formalism, the theory is only $\Z/2$ graded.

In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.

\parsec[s:fields]
The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.

\parsec[s:e510]

Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
\[
\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
\]

\parsec[s:L0]

For us, a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
\[
\ell_k \colon L^{\times k} \to \Pi^k L 
\]
are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}

Let $L_{sugra}$ be the following $\Z/2$ graded $L_\infty$ algebra. 
The even part is 
\[
\Vect (\Hat{D}^5) \oplus \cO (\Hat{D}^5) .
\]
We will denote even elements by $(\mu, \beta)$ according to the decomposition. 
The odd part is 
\[
\cO(\Hat{D}^5) \oplus \Omega^1(\Hat{D}^5) .
\]
We will denote odd elements by $(\nu, \gamma)$ according to the decomposition.

The $L_\infty$ structure is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1(\Hat{D}^5) \subset L_{sugra,-} \\
\d \mu & = \div \mu \in \cO(\Hat{D}^5) \subset L_{sugra, -}
\end{align*}
and $\d \gamma = \d \nu = 0$.

For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{sugra}$ with the structure of a $\Z/2$ graded $L_\infty$ algebra.

@@

By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.

On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
\[
\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
\]
The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
\[
\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
\]
which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$.

\begin{thm}[\cite{RSW}[Theorem 2.1]]
The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
\[
j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
\]
Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
\end{thm}

As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.

\begin{cor}
\label{cor:sugraops}
Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
There is a quasi-isomorphism of commutative dg algebras
\[
\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
\]
\end{cor}

@@

\parsec[]

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.

The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \mu + \dbar \Omega & = 0 \\
\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

@@

\parsec[s:zz2]

In the BV formalism the fields of a free theory together with the ghosts and the (partial) antifields combine to form a cochain complex.

\parsec[s:singleops]

\begin{prop}
Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
There is a quasi-isomorphism of super commutative dg algebras 
\[
\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
\]
\end{prop}
\begin{proof}
This follows from Lemma \ref{lem:localops}.
In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
\beqn
\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
\eeqn
and
\beqn
\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
\eeqn
The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
The differential is zero on the odd summand.
We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.

From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
\[
(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
\]
That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
\end{proof}

>>>>

@@

In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given.
Within the BV formalism, the theory is only $\Z/2$ graded.
In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory which we recall here.

The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.

%\parsec[s:e510]
%
%Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
%\[
%\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
%\]

\parsec[s:Lsugra]

In this paper a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
\[
\ell_k \colon L^{\times k} \to \Pi^k L 
\]
are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}

Let $L_X$ be the following sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau five-fold $X$.
As a sheaf of super vector spaces, $L_X$ is given as the holomorphic sections of a super vector bundle. 
The even part of this super vector bundle is
\[
\T_X \oplus \C_X 
\]
where $\T_X$ is the holomorphic tangent bundle and $\C_X$ is the trivial bundle.
We will denote even sections by $(\mu, \beta)$ according to the decomposition. 
The odd part is 
\[
\C_X \oplus \T^*_X .
\]
We will denote odd elements by $(\nu, \gamma)$ according to the decomposition.

The $L_\infty$ structure is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.

As all operations above are given in terms of holomorphic polydifferential operators, the $L_\infty$ algebra structure above induces a $\Z/2$ graded $L_\infty$ algebra structure on the Dolbeault resolution $\Omega^{0,\bu}(X,L_X)$ of the holomorphic vector bundle $L_X$.

Finally, to obtain a local $L_\infty$ algebra on $X \times S$, where $S$ denotes an arbitrary real oriented smooth one-manifold, we simply tensor with the de Rham complex along~$S$.
We denote by $\cL_{sugra}$ the following local $\Z/2$ graded $L_\infty$ algebra on $X \times S$
\beqn
\cL_{sugra} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(X,L_X) .
\eeqn

\parsec[s:rsw]
It is shown in \cite{RSW} that $\cL_{sugra}$ is equipped with a non-degenerate odd pairing which is compatible with the $L_\infty$ structure above. 
All together, this data prescribes the structure of a $\Z/2$ graded theory in the BV formalism. 
On $X \times S = \C^5 \times \R$ it is furthermore argued in \cite{RSW} that this BV theory is equivalent to the holomorphic (or minimal) twist of perturbative eleven-dimensional supergravity.

@@

The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
\[
U \subset S \times X 
\]
the cochain complex
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]

@@

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $Z$ (which is not necessarily equipped with a Calabi--Yau structure).
In the particular twist we will use we must assume, however, that $Z$ is equipped with a square-root of the canonical bundle $K_Z^{1/2}$.

The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\alpha \in \Omega^{2,1}(X), \quad \omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \alpha + \dbar \omega & = 0 \\
\dbar \alpha = \dbar \phi_i & = 0 .
\end{split}
\eeqn

@@

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\ZZ/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\leq 1, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]
The full space of BV fields is simply $\Pi \cL_{single}$.

\parsec[s:singleobs]

The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
\[
U \subset Z
\]
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]

The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting some number of fivebranes \brian{references}. 
In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting some number of holomorphically twisted fivebranes. 
We briefly recall the relevant setup here.

As above, let $Z$ be a three-fold equipped with $K^{1/2}_Z$.
Consider the rank two vector bundle $K^{1/2}_Z \otimes \C^2$ on $Z$. 
Via the linear holomorphic symplectic form on $\C^2$, the total space of this vector bundle ${\rm Tot}(K^{1/2}_Z \otimes \C^2)$ is equipped with a Calabi--Yau structure. 
We consider the eleven-dimensional theory on 
\[
\R \times {\rm Tot}(K^{1/2}_Z) 
\]
with a stack of fivebranes supported at $0 \in \R$ and along the zero section in the total space of the vector bundle
\[
0 \times Z \subset \R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)  .
\]
Let us denote $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$.

It was argued in \cite{RSW} that to leading order the coupling of a stack of twisted fivebranes to the eleven-dimensional theory is given by the nonlocal interaction 
\beqn\label{eqn:br1}
I_{M5} = N\int_{Z} \div^{-1}\mu \vee \Omega +\cdots 
\eeqn
where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.

\subsection{Supergravity at the boundary of AdS}

Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\RR \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
If we remove this locus we obtain the following manifold 
\[
\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
\]
where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.

\parsec[s:flat]

%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
%\[
%\C^3 \times (\R \times \C^2 - 0) .
%\]
%
%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.

In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.

Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
\[
\pi_* \Obs_{sugra} 
\]
on $\C^3$.
This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(t;\lambda w , z).
\]
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(t;\lambda w , z).
\]
\end{itemize}

For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.

\begin{prop}
For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$. 
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
\end{prop}

Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
\[
U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
\]
has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.

\begin{prop}
There is a natural inclusion of of factorization algebras 
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\end{prop}

We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.

\brian{old below}
